Meet the team

### 2023-09-22 team.qmd
update members on team page

**Hibaa Hasan**, Undergraduate thesis student (Psychology, Neuroscience, and Behaviour)  
**Lidia Barbera**, Undergraduate thesis student (Life Sciences)  
**Ola Schwarzenberg**, Undergraduate thesis student (Life Sciences - Sensory Motor Systems specialization)  
**Enuri Dissanayake**, Undergraduate practicum student (Life Sciences - Sensory Motor Systems specialization)

<!-- :::{#junior} -->
<!-- ::: -->

>>>>

:::{#junior}
:::

<!-- **Hibaa Hasan**, Undergraduate thesis student (Psychology, Neuroscience, and Behaviour)   -->
<!-- **Lidia Barbera**, Undergraduate thesis student (Life Sciences)   -->
<!-- **Ola Schwarzenberg**, Undergraduate thesis student (Life Sciences - Sensory Motor Systems specialization)   -->
<!-- **Enuri Dissanayake**, Undergraduate practicum student (Life Sciences - Sensory Motor Systems specialization)   -->
